---
title: "Ddyao-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Ddyao-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(DdyaoPackage)
```


### How to launch the app?

After you load the DyyaoPackage, you can launch the app by typing following command:

```{data format = "text", encoding = "asis", output.var = "df"}
launch_app()
```

### What the app does?

Generally, the app can provide some useful data visualtion about COVID19 in Italy.

### Guidelines for the app

#### Table
- You can click the top of the table(column name)to filter and arrange the case of COVID19 in Italy for each month.
the column name including month, MonthlyTotal, recovered, death, recovered rate and death rate. 
You can do your research in any combination you want.


#### Figure
- About the figure which is the province vs numbers of cases about each province.
on the left of the bottom, you can select the which month do you want to know the numbers of COVID19 case for each province.
on the other hand, in the poltly, you can click each bar to know the detail of each province for that.

#### Navigation
- In the middle of the page, you can see the navigation. you can select the about package to visit the introduction and the data analysis for the COVID19 with Italy.




